API design for machine learning software: experiences from the scikit-learn project

### 2013-06-27 paper.tex
trim introduction back to a page and a bit

From its core, the library has been designed to tie in with the set of numeric
and scientific packages centered around the NumPy and SciPy libraries. NumPy
\citep{vanderwalt2011} augments Python with a contiguous numeric array datatype
and fast array computing primitives,
while SciPy \citep{varoquaux2013scipy} extends it
further with common numerical operations, either by implementing
these in Python/NumPy or by wrapping existing C/C{}\verb!++!/Fortran
implementations. The \textit{scikits} were created to complement SciPy with
domain-specific toolkits. Currently, the two most popular and feature-complete
ones are by far \sklearn for machine learning and 
\textit{scikit-image}\footnote{\url{http://scikit-image.org}} for image
processing.

@@

In a previous paper \citep{pedregosa2011}, \sklearn was briefly presented and
benchmarked against several competitors. In this paper, we instead present an
in-depth analysis of design choices made when building the
library. We first present in section~\ref{sec:core-api} the central application
programming interface (API) and then describe, in section~\ref{sec:advanced-api},
advanced API mechanisms built on the core interface.
Section \ref{sec:implementation} briefly describes the implementation.
Section \ref{sec:comparison} then
compares \sklearn to other major projects in terms of API.
Section \ref{sec:future_work} outlines some of the work to be done before
a \sklearn 1.0 release.
Finally, we summarize and conclude in section \ref{sec:conclusions}.

>>>>

From its core, the library has been designed to tie in with the set of numeric
and scientific packages centered around the NumPy and SciPy libraries. NumPy
\citep{vanderwalt2011} augments Python with a contiguous numeric array datatype
and fast array computing primitives,
while SciPy \citep{varoquaux2013scipy} extends it
further with common numerical operations, either by implementing
these in Python/NumPy or by wrapping existing C/C{}\verb!++!/Fortran
implementations. The \textit{scikits} were created to complement SciPy with
domain-specific toolkits. Currently, the two most popular and feature-complete
ones are by far \sklearn and
\textit{scikit-image}\footnote{\url{http://scikit-image.org}} for image
processing.

@@

\citet{pedregosa2011} briefly presented \sklearn and
benchmarked it against several competitors.
In this paper, we instead present an
in-depth analysis of design choices made when building the library,
detailing how we organized and operationalized
common machine learning concepts.
We first present in section~\ref{sec:core-api} the central application
programming interface (API) and then describe, in section~\ref{sec:advanced-api},
advanced API mechanisms built on the core interface.
Section \ref{sec:implementation} briefly describes the implementation.
Section \ref{sec:comparison} then
compares \sklearn to other major projects in terms of API.
Section \ref{sec:future_work} outlines some of the work to be done before
a \sklearn 1.0 release.
We summarize and conclude in section \ref{sec:conclusions}.
